VariantSpark: Population Scale Clustering of Genotype Information

### 2015-09-17 doc/publications/journal2014/paper.tex
Added Gephi citation; cluster visualization = figure 3; some text for graph visualization

\subsection*{Graph visualization}
Add the image here \ldots

@@

\begin{figure}[h!]
  \caption{\csentence{Sample figure title.}
      Figure legend text.}
      \end{figure}

>>>>

\subsection*{Graph visualization}
%% Add the image here \ldots
A visualization of the clusters generated by \variantSpark{} from 1000 Genomes Project data, generated using Gephi \cite{ICWSM09154}, is 
shown in Figure 3. Three of the four clusters (super-populations AFR, EAS and AMR) are relatively-homogeneous; the fourth is more mixed and 
consists predominantly of individuals labelled EUR and AMR.

@@

\begin{figure}[h!]
\includegraphics[type=pdf,ext=.pdf,read=.pdf, scale=0.25]{chr22-k4-gephi}
  \caption{\csentence{Visualization of \variantSpark{} clusters.} Individuals from the 1000 Genomes project are clustered effectively by super-populations AFR, AMR and EAS; a fourth cluster is predominantly EUR + AMR.}
      \end{figure}
